Visual Geo-Localization: mapping images to GPS

### 2023-02-03 paper/paper.tex
paper updated

\textbf{Augmentation Pipeline.}
Due to the high computational requirements, we were only able to conduct this ablation efficiently on SF-XS dataset with a low amount of iterations per epochs fixed to 5000. The results reporting recalls are reported in the table \ref{tab:augmentations-pp} below:

@@

\begin{table}[hbp] % Add the following just after the closing bracket on this line to specify a position for the table on the page: [h], [t], [b] or [p] - these mean: here, top, bottom and on a separate page, respectively
\centering % Centers the table on the page, comment out to left-justify
\begin{tabular}{l c c c c c} % The final bracket specifies the number of columns in the table along with left and right borders which are specified using vertical bars (|); each column can be left, right or center-justified using l, r or c. To specify a precise width, use p{width}, e.g. p{5cm}
\toprule % Top horizontal line
Augmentations & R@1 & R@5 & R@10 & R@20\\ % Column names row
\midrule % In-table horizontal line
Base & 1.0\%  & 1.6\% & 1.9\% & 2.0\%  \\ 
+\{blur\} & 1.2\%  & 1.8\% & 2.0\% & 2.0\%  \\ 
+\{grayscale\} & 1.2\%  & 1.7\% & 1.9\% & 2.0\%  \\ 
+\{flip\} & 1.0\%  & 1.7\% & 1.8\% & 1.9\%  \\  
+\{erasing\} & 1.2\%  & 1.9\% & 1.9\% & 1.9\%  \\  
+\{grayscale, erasing\} & 1.1\%  & 1.9\% & 1.9\% & 2.0\%  \\  
+\{blur, grayscale\} & 1.1\%  & 1.9\% & 2.0\% & 2.0\%  \\  
+\{\textbf{blur, erasing}\} & 1.2\%  & 1.9\% & 2.0\% & 2.0\%  \\  
+\{blur, grayscale,\\ flip, erasing\} & 1.0\%  & 1.7\% & 2.0\% & 2.0\%  \\

@@

The couple \textbf{blur, erasing} seems the best choice for the augmentation pipeline, since not only the model manages to show robustness to that data augmentation pipeline, but also improves.
However, further investigations should be performed with a larger amount of data and a higher amount of iterations to understand if this is an improvement linked to a better generalization due to the lack of data. 
[TODO guardare extension b]
\newline

@@

>>>>

\textbf{Augmentation Pipeline.}
Due to the high computational requirements, we were only able to conduct this ablation efficiently on SF-XS dataset with a low amount of iterations per epochs fixed to 5000 and a batch size reduced to 16 instead of respectively 10000 and 32 as the default model. The results reporting recalls are presented in the table \ref{tab:augmentations-pp} below:

@@

\begin{table}[hbp] % Add the following just after the closing bracket on this line to specify a position for the table on the page: [h], [t], [b] or [p] - these mean: here, top, bottom and on a separate page, respectively
\centering % Centers the table on the page, comment out to left-justify
\begin{tabular}{l c c c c c} % The final bracket specifies the number of columns in the table along with left and right borders which are specified using vertical bars (|); each column can be left, right or center-justified using l, r or c. To specify a precise width, use p{width}, e.g. p{5cm}
\toprule % Top horizontal line
Augmentations & R@1 & R@5 & R@10 & R@20\\ % Column names row
\midrule % In-table horizontal line
Base & 43.9\%  & 61.7\% & 67.0\% & 71.2\%  \\ 
+\{blur\} & 44.2\%  & 60.4\% & 67.3\% & 70.8\%  \\ 
+\{grayscale\} & 45.6\%  & 60.9\% & 67.4\% & 70.7\%  \\ 
+\{flip\} & 43.8\%  & 62.0\% & 68.0\% & 71.9\%  \\  
+\{erasing\} & 44.0\%  & 59.8\% & 65.0\% & 70.2\%  \\  
+\{grayscale, erasing\} & 43.4\%  & 59.2\% & 65.2\% & 70.1\%  \\  
+\{blur, grayscale\} & 45.9\%  & 61.3\% & 68.6\% & 70.9\%  \\  
+\{blur, erasing\} & 43.8\%  & 60.2\% & 65.3\% & 70.4\%  \\  
+\{blur, grayscale,\\ flip, erasing\} & 43.6\%  & 59.1\% & 64.8\% & 70.4\%  \\

@@

The couple of augmentation \textbf{blur, grayscale} seems the best choice for the augmentation pipeline, since not only the model manages to show robustness to that data augmentation pipeline, but also gets improvements.
Further investigations should be performed with different parameters to deeply understand those results, however it seems that grayscale performs better since it show invariance to the colors of the scenes changing through the day. [TODO valutare se aggiungere ref.]
[TODO guardare extension b]
\newline

@@

\textbf{Qualitative Evaluation with Top K-NN}
\newline 
To assess the goodness of the results obtained applying FDA and GRL in particular on Tokyo-Night dataset, we look at the nearest neighbors in the feature space, to understand the trained model's reasoning on different proposed queries. 
Therefore, we built a top K - Nearest Neighbors visualization
for which given a query image, the K closest points in the learning embedding space are retrieved.
In order to retrieve the top K = 5 most similar images to a given one, we calculate the Euclidean distance between the target image's embedding and each image's embedding in the dataset, one by one.
For our experiment, we used and tested Tokyo-Night [TODO REF] as database for the queries retrieval in fig. \ref{fig:tokyonighttopknn} in two different ways.
The model was trained with FDA and GRL active [TODO review..], however in the set A)\newline we didn't apply FDA to the images just to be sure that our trained model worked as intended with the original set both on day and night queries and the result was perfect for the first 3 neighbors.
In the set B) we applied FDA to the dataset and used as query the same image treated with FDA (on the left) and another among its correct night queries (on the right).
Once again the result was satisfactory and the FDA-treated image was perfectly recognized and integrated in both cases, proving the correct reasoning of our proposed model.

\begin{figure*}
  \centering
  \begin{subfigure}{1.0\linewidth}
    \centering
    \fbox{ \includegraphics[width=\dimexpr\textwidth-2\fboxrule-2\fboxsep]{assets/topknn.png}}
    \caption{2a TODO CAPTION, attention to ref}
    \label{fig:tokyonighttopknn}
  \end{subfigure}
  \hfill
\end{figure*}
